---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# searchterms

<!-- badges: start -->
<!-- badges: end -->

The goal of searchterms is to identify overrepresented terms in a set of relevant references for a systematic review, which can be applied in a boolean search.

## Installation

You can install the development version of searchterms from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("claudiakapp/searchterms")
```
## Statistics
The test statistic is a binomial test, which is implemented in the internal function "calculate_z_scores()" and defined with:

  x = observed frequency of each unique term, merged\$testset_freq  
  n = Sample size, the amount of all terms in the sample, merged\$n  
  p = expected frequency of each unique term in the norm population 
  erwarteten Häufigkeit (aus dem Referenzpool bestimmt), merged\$p  
  
The expected frequency in the sample is approximated with n\*p and the variance with n\*p\*(1-p). The z-score is calculated with: (x – n\*p) / sqrt( n\*p\*(1-p) )


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(searchterms)
path <- system.file("extdata", "example_ris.txt", package= "searchterms", mustWork = T)
data <- z_scores(path)
head(print_z_scores(data, terms = "freetext") )
head(print_z_scores(data, terms = "MeSH"))
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

